# Organ Association

To assess how each protein's expression associates with the severity of the disease in different organs, correlation coefficients were calculated between each protein's NPX value and the organ scores. The resulting p-values were corrected for multiple testing using the Benjamini-Hochberg procedure.

## Plasma

The full list of protein-wise Pearson correlation results for the different organs is collected in excel files in **Results/Plasma/Organ/[organ]/[organ]_pearson_correlation.xlsx**. In addition, the partial correlation coefficients (i.e. correlation when NPX values are adjusted for age and ckd_epi) can be found in **Results/Plasma/Organ/[organ]/[organ]_pearson_correlationn_adjusted_age_ckd_epi.xlsx**. These results are quite similar to the unadjusted correlation coefficients but are added here if they would be needed later. All individuals regressions are plotted and collected in the subfolder **regression_plots/**. 

The unadjusted results are also shown here in an interactive table. Results are ranked by adjusted p-value and a link to the corresponding plot is added. 

```{r}
create_organ_table <- function(source = "Plasma", organ = "general") {
  
  readxl::read_excel(paste0("~/Results/", source, "/Organ/", organ, "/", organ, "_pearson_correlation.xlsx")) %>%
  dplyr::select(-c(method, alternative)) %>%
  mutate_if(is.numeric, round, 4) %>%
  mutate("plot" = paste0('<a href ="./../Results/', source, '/Organ/', organ, '/regression_plots/', Assay, '_regression.pdf"  target="_blank">', Assay, '</a>')) %>%
  datatable(class = 'cell-border stripe compact', 
            extensions = 'Buttons', 
            options = list(
              dom = 'Bfrtip',
              buttons = c('copy', 'csv', 'excel', 'pdf')),
            escape = FALSE)
  
}
```

::::: {.panelset}

::: {.panel}
[General]{.panel-name}

```{r pl_gen}
create_organ_table("Plasma", "general")
```
:::

::: {.panel}
[Cutaneous]{.panel-name}

```{r pl_cut}
create_organ_table("Plasma", "cutaneous")
```
:::

::: {.panel}
[Muc_memb_eyes]{.panel-name}

```{r pl_muc}
create_organ_table("Plasma", "muc_memb_eyes")
```
:::

::: {.panel}
[Ent]{.panel-name}

```{r pl_ent}
create_organ_table("Plasma", "ent")
```
:::

::: {.panel}
[Chest]{.panel-name}

```{r pl_chest}
create_organ_table("Plasma", "chest")
```
:::

::: {.panel}
[Cardiovascular]{.panel-name}

```{r pl_card}
create_organ_table("Plasma", "cardiovascular")
```
:::

::: {.panel}
[Abdominal]{.panel-name}

```{r pl_ab}
create_organ_table("Plasma", "abdominal")
```
:::

::: {.panel}
[Renal]{.panel-name}

```{r pl_ren}
create_organ_table("Plasma", "renal")
```
:::

::: {.panel}
[Nervous_System]{.panel-name}

```{r pl_nerve}
create_organ_table("Plasma", "nerv_system")
```
:::

::: {.panel}
[Final_Score]{.panel-name}

```{r pl_fin}
create_organ_table("Plasma", "final_score")
```
:::

:::::


## Serum

The full list of protein-wise Pearson correlation results for the different organs is collected in excel files in **Results/Serum/Organ/[organ]/[organ]_pearson_correlation.xlsx**. In addition, the partial correlation coefficients (i.e. correlation when NPX values are adjusted for age and ckd_epi) can be found in **Results/Plasma/Organ/[organ]/[organ]_pearson_correlationn_adjusted_age_ckd_epi.xlsx**. These results are quite similar to the unadjusted correlation coefficients but are added here if they would be needed later. All individuals regressions are plotted and collected in the subfolder **regression_plots/**. 

The unadjusted results are also shown here in an interactive table. Results are ranked by adjusted p-value and a link to the corresponding plot is added. 

::::: {.panelset}

::: {.panel}
[General]{.panel-name}

```{r ser_gen}
create_organ_table("Serum", "general")
```
:::

::: {.panel}
[Cutaneous]{.panel-name}

```{r ser_cut}
create_organ_table("Serum", "cutaneous")
```
:::

::: {.panel}
[Muc_memb_eyes]{.panel-name}

```{r ser_muc}
create_organ_table("Serum", "muc_memb_eyes")
```
:::

::: {.panel}
[Ent]{.panel-name}

```{r ser_ent}
create_organ_table("Serum", "ent")
```
:::

::: {.panel}
[Chest]{.panel-name}

```{r ser_chest}
create_organ_table("Serum", "chest")
```
:::

::: {.panel}
[Cardiovascular]{.panel-name}

```{r ser_card}
create_organ_table("Serum", "cardiovascular")
```
:::

::: {.panel}
[Abdominal]{.panel-name}

```{r ser_ab}
create_organ_table("Serum", "abdominal")
```
:::

::: {.panel}
[Renal]{.panel-name}

```{r ser_ren}
create_organ_table("Serum", "renal")
```
:::

::: {.panel}
[Nervous_System]{.panel-name}

```{r ser_nerve}
create_organ_table("Serum", "nerv_system")
```
:::

::: {.panel}
[Final_Score]{.panel-name}

```{r ser_fin}
create_organ_table("Serum", "final_score")
```
:::

:::::