# Correlation

Pearson correlations of each protein versus crp, sr and bvas values were calculated.

## crp

The full list of protein-wise pearson correlation results with crp is collected in excel files in **Results/Plasma/Correlation/crp/crp_pearson_correlation.xlsx** and **Results/Serum/Correlation/crp/crp_pearson_correlation.xlsx**

All individuals regressions are plotted and collected in the subfolder **regression_plots/** (see Figure \@ref(fig:crpCorr))

```{r crpCorr, fig.show='hold', out.width="49%", fig.align='center', fig.cap="Most significant positively crp correlated protein (Left) Most significant negatively crp correlated protein (Right). Indicated in red is the pearson correlation coefficient and 95% confidence interval in grey"}
knitr::include_graphics(c("../Results/Plasma/Correlation/crp/regression_plots/IL6_regression.pdf", "../Results/Plasma/Correlation/crp/regression_plots/SCF_regression.pdf"))
```

## sr

The full list of protein-wise pearson correlation results with sr is collected in excel files in **Results/Plasma/Correlation/sr/sr_pearson_correlation.xlsx** and **Results/Serum/Correlation/sr/sr_pearson_correlation.xlsx**

All individuals regressions are plotted and collected in the subfolder **regression_plots/** (see Figure \@ref(fig:srCorr))

```{r srCorr, fig.show='hold', out.width="49%", fig.align='center', fig.cap="Most significant positively sr correlated protein (Left) Most significant negatively sr correlated protein (Right). Indicated in red is the pearson correlation coefficient and 95% confidence interval in grey"}
knitr::include_graphics(c("../Results/Plasma/Correlation/sr/regression_plots/CCL23_regression.pdf", "../Results/Plasma/Correlation/sr/regression_plots/SCF_regression.pdf"))
```

## bvas

The full list of protein-wise pearson correlation results with bvas is collected in excel files in **Results/Plasma/Correlation/bvas/bvas_pearson_correlation.xlsx** and **Results/Serum/Correlation/bvas/bvas_pearson_correlation.xlsx**

All individuals regressions are plotted and collected in the subfolder **regression_plots/** (see Figure \@ref(fig:bvasCorr))

```{r bvasCorr, fig.show='hold', out.width="49%", fig.align='center', fig.cap="Most significant positively bvas correlated protein (Left) Most significant negatively bvas correlated protein (Right). Indicated in red is the pearson correlation coefficient and 95% confidence interval in grey"}
knitr::include_graphics(c("../Results/Plasma/Correlation/bvas/regression_plots/GDF-15_bvas_correlation.pdf", "../Results/Plasma/Correlation/bvas/regression_plots/IL-1 alpha_bvas_correlation.pdf"))
```
